First Detection of the Environmental Dependence of the Structures of Massive Galaxies

### 2016-12-04 draft/ms_v1.tex
version 0

% Packages
%\usepackage{emulateapj5}
\usepackage{apjfonts}
\usepackage{amssymb, amsmath}
\usepackage{graphicx}
\usepackage{CJK}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{float}
\usepackage[usenames]{color}

@@

% Commenting:
\newcommand{\xxx}[1]{\textcolor{red}{\textbf{XXX}}}
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}

@@

\title{First Detection of the Enviromental Dependence of the Masses, Sizes, and Structures of Massive Galaxies }

\author{Song Huang (黄崧)\altaffilmark{1}, 
        HSC collaboration\altaffilmark{1}}

%        \author{Song Huang (黄崧)\altaffilmark{1} 
%        Alexie Leauthaud\altaffilmark{1}, 
%        Kevin Bundy\altaffilmark{1},
%        Michael Strauss\altaffilmark{2},
%        Yen-Ting Lin\altaffilmark{3},
%        Rachel Mandelbaum\altaffilmark{4}
%        }

@@

\altaffiltext{1}{Kavli Institute for the Physics and Mathematics of the 
    Universe, The University of Tokyo Institutes for Advanced Study, 
    the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan}

%\altaffiltext{2}{Princeton University Observatory, 
%    Peyton Hall, Princeton, NJ 08544, USA}
%\altaffiltext{3}{Institute of Astronomy and Astrophysics, Academia Sinica, 
%    P.O.~Box 23--141, Taipei 10617, Taiwan}
%\altaffiltext{4}{Carnegie-Mellon University \todo{correct affiliation here}}

@@

@@

\alexie{Because the text is long, at this point in the introduction, let's give reader an overview of our methodology. Let's sim for one or two succint paragraphs. That way they will begin the paper having a better idea of what we want to achieve. We will want to give them some key ideas here. 1) Quality of the HSC data (Reference Fig 1 here) 2) we want to look for enviromental differences, we'll use  a cluster catalog to divide into halo mass bins, 3) define the concepts of M10 and M100 (and reference Fig 10 here). You sort of have the elements in place below, by needs more editing and reorganizing.}

\alexie{Bring Fig 1 and Fig 10 here so they are the two first figures.}

	\song{Ok, will do; I will just say Fig 10 demonstrate the stellar mass and structural 
    	diversity of the massive galaxies}

    To achieve this goal, we select a large sample of massive central galaxies within
    halos that are more or less massive than \logmh{}$\sim 14.0$ at $0.3 < z < 0.5$ 
    from the current $\sim 100$ square degree of HSC data.
    As indicated by the $M_{\star}$-$M_{\mathrm{Halo}}$ relation, at the same \mstar{}, 
    massive central galaxies with similar morphology can live in halos within large range 
    of \mhalo{}, therefore it is very interesting to look into the influence of their halos 
    on the structure of these galaxies. 
    Under the adopted cosmology, $1.0^{\arcsec}$ equals 4.4 and 6.1 kpc at redshift 0.3 
    and 0.5.  
    In this redshift range, we can reliably measure the total stellar mass within the 
    inner 5 to 10 kpc (where the ``in-situ'' stellar component should dominate) given 
    the typical seeing, while still be able to map their stellar distributions out to 
    $\sim 100$ kpc at $z\sim 0.5$ given the imaging depth of these HSC data.
    Also, we can safely ignore significant mass growth and structural evolution 
    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
    \citealt{Inagaki2015}; but also see \citealt{Bai2014}) 
    with our redshift and \mstar{} ranges.

@@

    Because of the caveats that apply to \texttt{hscPipe} measurements for bright 
    galaxies, we will use custom made software to measure the luminosity profiles of
    massive galaxies. 
    Our first step is use the HSC galaxy catalog to create an initial sample of massive
    galaxies that is complete to \xxx{} at $z < 0.5$. 
    We will then use custom made software to re-measure luminosities for all galaxies 
    in this sample. 
    Based on Leauthaud\etal~(2016), most \logms{}$\geq 11.5$ galaxies should have 
    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag.
    So we first select all galaxies with $i_{\mathrm{HSC, cModel}} \leq 21.5$ 
    \footnote{We neglect the insignificant differences between the response curves of
    SDSS-$i$ and HSC-$i$ filters}
    in regions that have reached the required depth of \texttt{WIDE} survey in all 
    five bands. 
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects

@@

    Among the 116813 matched objects, 42696 are at $0.2 \leq z \leq 0.5$.
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    The majority of these redshifts come from either SDSS or BOSS data.  
    GAMA survey contributes another $\sim 14$\%. 
    For objects without external spec-$z$, we match them with the central galaxies 
    from \redm{} catalog using $2.0^{\arcsec}$ radius. 
    The matched objects with useful red-sequence photo-$z$ ($z_{\lambda}$) are also 
    included in the final sample of bright galaxies with reliable redshift between 
    $0.2 \leq z \leq 0.5$
    (will be referred as \texttt{hscZ}).
    As we will show later (see Section \ref{ssec:future}), to ensure reasonable 
    \mstar{}-completeness at the high-\mstar{} end, and make sure the samples we 
    want to compare have well overlapped redshift distributions, we will focus on 
    the galaxies at $0.3 \leq z \leq 0.5$.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[bt!]
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_smf_new}
      \caption{\textbf{Left:}: We compre the \mstar{} volume-density distributions of 
      	  \rbcg{} (red) and \nbcg{} (black) galaxies using stellar mass based on 
          \mcmodel{} (dash) and \mtot{} (solid) to highlight the increase of \mstar{}
          due to different methods.  
          Here we also show the volume-density distributions of the \texttt{S82-MGC} 
          galaxies (green) to evaluate the \mstar{}-completeness. 
          The vertical line highlight \logms{}$=11.6$ before correcting the \mstar{} using
          total luminosity from 1-D profile.~~
          \textbf{Right:} We plot \mtot{} against the difference between \mtot{} and 
          \mcmodel{} for the \rbcg{} (red squares; color indicates redshift) and \nbcg{}
          (grey dots) galaxies. 
          Two vertical lines highlight the $11.6<$\logmtot{}$<11.9$ mass range where the
          two samples overlap the most.
          We also show the historgrams of the mass differences for galaxies with 
          $11.6<$\logmtot{}$<11.9$ on the right side. 
          \song{The figure is updated, but I think the histogram on the right side is 
          useful; 1) it shows the average mass difference clearly; 2) shows the differences
          between the two samples; Also try to update the caption, let me know what do you 
          think. And, I think the left panel should stay here, because we need to discuss 
          the mass completness here; the discussion section can use another figure where 
          we overplot other people's SMF; we just need some caveats.}
          \alexie{Simplfy the caption here. What is the main message we are trying to convey. 
          I think the point of this figure is to show that cmodel is underestimated. 
          Focus on that message. Some information here is un-necessary. 
          Also looks make some changes to this Figure: 1) right. Remove the right hand 
          histograms. 2) I ont think we learn much by the color coding. Just use a single 
          color (less explaning to do). Label using your names cenLowMh and cenHighMh}}
      \label{fig:smf1}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    Assuming that the \redm{} catalog correctly identifies all halos with 
    $M_{200m}\sim 1.0\times 10^{14} h^{-1} M_{\odot}$ in the current footprint,
    the unmatched massive galaxies from the above step should be dominated by central 
    galaxies of less massive halos and massive satellites galaxies.  
    To select a purer sample of massive centrals in $M_{200m}<10^{14} h^{-1} M_{\odot}$
    halos, we identify and remove any galaxy that is too close to 
    \emph{any cluster member} in \redm{} catalog in both radius and redshift direction.

    \alexie{This is a rather strange procedure, I think we need to change it (referee and readers will complain!). What we really want to do is to remove any galaxies that have $r<R200$ in projection (from the galaxy with the highest value of Pcen) and remove galaxies within some deltaz of the cluster redshift. The cluster redshift is more well determined than the redshift estiamte of any cluster member. In short, what we are doing here is cutting out a cylindar arond the most likley BCG. The deltaz value can be motivated by the cluster redshift uncertainty from the redmapper papers. The only remaining question is then what radius to use around clusters. To get that number here is what we need to do. 1) Start with Eq 12 and Table 3 in Simet et al. For each cluster, assign a value of M200m (halo mass defined as 200 time background) to each cluster. 3) we then need to estimate the cluster radius R200m (or R200b, same thing). To do this, we need to use a mass-concentration relation. I'm pretty sure there is an easy command to do this in Python using the python package "colossus" by bendikt diemer. Download it and see if youc an get it to work. If it doens't look obvious after 30 min, I can do it on my end using my own code. But good for you to know how to do this. We can simply use the mass-concentration realtion from Benedikts work. 4) Now for every cluster you have R200m. And you define the low halo mass central sample as ones that are not within any cylindar around any cluster. Sorry, I know this might mean re-doing everything.....let's discuss by Skype if this is a major issue.}

    For each \redm{} cluster member, we remove objects within a cylinder region 
    around it from the remaining sample. 
    Such cylinder is defined by 1) physical radius of 3.0 Mpc at the red-sequence 
    redshift of the cluster; 2) $|z - z_{\lambda}| \leq 0.05$ as 
    \nbcg{} later.

@@

    \begin{itemize}
        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
            with $i_{\mathrm{cModel}} \leq 21.0$, good quality images and reliable 
            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
            data release. 
        \item \texttt{hscZ} sample: through matching the \texttt{hscPho} sample with 
            spectroscopic redshifts from surveys like SDSS/BOSS and GAMA, or accurate 
            red-sequence photometric redshift in the \redm{} catalog, we come up with 
            a large sample of bright galaxies with reliable redshift information. 
        \item \rbcg{} sample: we select a sample of 375 galaxies at $0.2 \leq z \leq 0.5$
            that are identified as central galaxies in $\lambda > 30$ \redm{} clusters. 
            The most reliable ones ($P_{\mathrm{Cen}} >0.7$) among 
            them will represent the central galaxies in very massive halos
            (\logmh{}$\geq 14.0$). 
        \item \nbcg{} sample: after excluding all the galaxies that are close to any 
            \redm{} clusters in both radial and redshift directions from the 
            \texttt{hscZ} sample, we have 29973 bright galaxies at $0.2 \leq z \leq 0.5$.
            With the help of \mstar{} estimates via SED fitting (see Section 
            \ref{ssec:isedfit}), we consider the massive ones among them as the 
            candidates of central galaxies in halos with \logmh{}$<14.0$.  
        \item To compare the \rbcg{} and \nbcg{} samples carefully, we will focus on 
            the redshift range at $0.3 \leq z \leq 0.5$ where their redshift 
            distributions greatly overlap and both samples have acceptable
            \mstar-completeness (see Section \ref{ssec:s82}).  
            Also, during the comparison of structures, we will mainly 
            \song{Will use $>30$ sample as default later; will update the figure first, 
            then correct the number of galaxies when I go through the text again.}
            \alexie{Why mainly use here? We have defined the high mass sample to be above this cut. Lets use $\lambda>30$ everywhere! Making more samples will make readers confused.} use \rbcg{} 
            galaxies with $\lambda > 30$ to ensure that they are from more massive 
            halos than the ones in \nbcg{} sample.
    \end{itemize}

@@

    Finally, we run \texttt{Ellipse} on the background-corrected image following similar 
    strategy of \citep{Li2012}.
    In short, we start with free centroid and shape of each isophote, then gradually 
    constrain their behaviors, and eventually extract 1-D surface brightness profile 
    along the major axis using isophotes with fixed centroid and shape.
    The 4th Fourier modes are included to fit the isophote better. 
    In this way, we can extract the radial changes of the centroid, ellipticity, 
    position angle, and average isophotal distortions (more ``disky'' or ``boxy'', 
    e.g.\ \citealt{Kormendy2009}) along with the surface brightness profile.  
    Fig.\ref{fig:ellipse} shows an example of the 1-D surface brightness and 
    ellipticity profile for a massive galaxy at $z\sim0.2$ along with its masked 
    image and a subset of isophotes.  
    Appendix\ref{app:A} includes more details about the \texttt{Ellipse} procedure.

@@

    We construct five band SED using the forced-photometry \cmodel{} magnitude corrected 
    for the Galactic extinction. 
    As for the photometric error, the current \cmodel{} photometry underestimates 
    the flux errors of bright galaxies as it only includes statistical error, not the 
    systematic uncertainties in the model-fitting process.  
    From tests of synthetic objects, we find that the average accuracy of \cmodel{} 
    photometry for bright galaxy is roughtly at 1\% level. 
    Therefore, we supply \texttt{iSEDFit} with simplified flux errors assuming $S/N = 100$ 
    for $riz$ bands, and $S/N = 80$ for $gY$ bands (on average, images in $gY$ bands are 
    shallower in depth and/or have higher background noise).  
    The typical uncertainty of \logms{} for both samples is around 0.08-0.10 dex at the 
    high-\mstar{} end. 
    Please see Appendix\ref{app:B} for more detailed discussions of the SED fitting
    results.  
    %In Fig.~3, we show an example of SED fitting result. 
    %\song{Not sure if we need to show one example, but put one here for now.}

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[t!]
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_sample_stats}
      \caption{\textbf{Left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
          (red circle; detaield format is the same with the right panel of 
          Fig.\ref{fig:smf1}) and \nbcg{} (grey dots) samples.
          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~
          \textbf{Middle}: the histograms of \mtot{} for the \rbcg{} (orange-red) and 
          \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
          $0.3 \leq z \leq 0.5$ (stepped histogram). 
          The vertical lines in both left and middle figures highlight the 
          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
          the \mtot{}-matched samples.~~
          \textbf{Right}: the histograms of the redshift for the \rbcg{} and 
          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
          mass bins.
          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range 
          \song{Will move to new Appendix later; but the figures are updated here; 
          I will make sure to use consistent symbols, colors, and legends.}
          \alexie{Move this figure to the appendix. It is not clear to be that we need this Figure anyway. We can say that we make matched samples in the text. I think that is enough. If the referee wants to see the Figure, we can show him or her. But I think it just adds clutter.}.
      }
      \label{fig:sample_stats}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    Using the best-fit stellar mass from \texttt{iSEDFit} (referred as \mcmodel{}), 
    we estimate the average \m2l{} in $i$-band, then use that \m2l{} to convert the 
    1-D luminosity density profiles into stellar mass density profiles; and 
    also convert the luminosity within 10 and 100 kpc apertures into 
    corresponding stellar mass estimates (referred as \minn{} and \mtot{}). 
    From now, we use \mtot{} as the new proxy of ``total'' stellar mass of these 
    galaxies.  
    And we also derive the $k$-corrected luminosity and colors from the results.
    In Appendix\ref{app:B}, we also show the outputs like the average stellar age, 
    metallicity, and internal dust extinction all behave reasonably for both 
    samples, but will not use them for further scientific analysis.

@@

    And, we should mention that our approach is in principle very similar to the 
    one adopted by the GAMA survey (\citealt{Taylor2011}), where they start with 
    \mstar{} estimated using average \m2l{} from SED fitting results of
    PSF-matched aperture photometry, and later correct it with better estimate 
    of total luminosity.  
    However, the GAMA survey relied on multi-band single-\ser model fitting on 
    the SDSS images to get total luminosity (\citealt{Kelvin2012}). 
    It is therefore interesting to compare the \mstar{} (\mgama{} v.s. \mtot{})
    estimates for galaxies in common, given the differences in data and method. 
    Please see the Appendix\ref{app:C} for more details. 
    In short, we notice systematic differences between the two \mstar{} estimates, 
    and it is likely that the GAMA models miss fluxes in the stellar halo that 
    is beyond the depth of SDSS image.

>>>>

% Packages
%\usepackage{emulateapj5}
\usepackage{apjfonts}
\usepackage{amssymb, amsmath}
\usepackage{graphicx}
\usepackage{CJK}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{float}
\usepackage[usenames, dvipsnames]{color}

@@

% Commenting:
\newcommand{\xxx}[1]{\textcolor{red}{\textbf{XXX}}}
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
\newcommand{\update}[1]{\textcolor{Bittersweet}{#1}}

@@

\title{First Detection of the Environmental Dependence of the Structures of Massive Galaxies }

\author{Song Huang (黄崧)\altaffilmark{1}, 
        HSC collaboration\altaffilmark{1}}   
%        \author{Song Huang (黄崧)\altaffilmark{1} 
%        Alexie Leauthaud\altaffilmark{1}, 
%        Kevin Bundy\altaffilmark{1},
%        Michael Strauss\altaffilmark{2},
%        Yen-Ting Lin\altaffilmark{3},
%        Rachel Mandelbaum\altaffilmark{4}
%        }

@@

\altaffiltext{1}{Kavli Institute for the Physics and Mathematics of the 
    Universe, The University of Tokyo Institutes for Advanced Study, 
    the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan}
%\altaffiltext{2}{Princeton University Observatory, 
%    Peyton Hall, Princeton, NJ 08544, USA}
%\altaffiltext{3}{Institute of Astronomy and Astrophysics, Academia Sinica, 
%    P.O.~Box 23--141, Taipei 10617, Taiwan}
%\altaffiltext{4}{Carnegie-Mellon University \todo{correct affiliation here}}

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[t!]
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
      \caption{Three-color images for a subsample of massive galaxies at similar redshift
      		($\sim 0.4$), and with similar \mstar{} inside inner 10 kpc (indicated by the 
            dash-line cicle on top-left figure; 
            $11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
            However, they span quite a large range in \mstar{} within 100 kpc 
            (highlighted by the solid bar on the top-left figure). 
            From top-left to bottom-right, their \mtot{} increases from 
            $10^{11.2} M_{\odot}$ to $10^{11.7} M_{\odot}$.
            The three galaxies from \rbcg{} sample are highlighted via red frames.
            }
      \label{fig:m100_m10_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    \update{Here, we take advantage of the excellent image quality of the HSC survey, and 
    investigate the potential environmental dependence of structure for massive galaxies 
    vial comparing the surface \mstar{} density profiles and structural scaling relations 
    between massive central galaxies in different environments. 
    As shown in Fig.\ref{fig:sdss_compare}, the HSC $i$-band images are typically 3-4 
    magnitude deeper than SDSS ones, and have much better seeing condition 
    (median FWHM$\sim 0.6^{\arcsec}$), hence they are perfect for mapping the \mstar{}
    distributions of massive galaxies out to very large radius. 
    With the help of a cluster catalog, we select a large sample of massive central 
    galaxies in halos that are more or less massive than \logmh{}$\sim 14.0$ at 
    $0.3 < z < 0.5$ from the available $\sim 100$ square degree of HSC data.}

    \update{Due to the difficulty in appropriately modeling the \mstar{} distributions of 
    massive galaxies out to their very outskirts, we focus on \mstar{} within two different 
    physical apertures in this work:}

    \begin{itemize}
        \item \update{\mstar{} within 10 kpc, \minn{}: according to the ``two-phase'' 
            scenario, the ``in-situ'' star-formation quickly built up the inner, dense 
            core of massive ETGs.  
            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
            \citealt{RodriguezGomez2016}), the in-situ 
            component distributes mostly within the effect radius ($R_{\mathrm{e}}$, 
            or 5-10 kpc) in massive galaxies.  
            Here we use \minn{} as a proxy of the \mstar{} formed in the ``in-situ''
            phase.  Although it is an empirical choice, the detailed comparison of 
            \mden{} profiles later suggests it indeed helps reveal interesting 
            environmental dependence.  
            Under the adopted cosmology, $1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
            at redshift 0.3 and 0.5.  
            We can reliably measure \minn{} without being bothered by smearing effect
            of seeing.}
        \item \update{\mstar{} within 100 kpc, \mtot{}: for massive galaxies in this work, 
            100 kpc aperture reaches to 5-10 $\times R_{\mathrm{e}}$ and very low 
            \mden{} region, hence can be treated as proxy of the ``total'' \mstar{}. 
            Limited by the accuracy of background subtraction, the \mden{} profile 
            of outer region can not be reliably recovered for massive galaxies across 
            our redshift range. 
            Although not perfect, \mtot{} is still a much better tracer of total 
            \mstar{} than the model-dependent ones using shallower images.}
    \end{itemize}

    \update{Massive central galaxies in this work show an intriguing diversity on the 
    plane defined by these two metrics.  
    We preview this using Fig.\ref{fig:m100_m10_color}, which shows a subsample of 
    massive galaxies at $z\sim 0.4$ that share very similar value of \minn{}, but show 
    a large range of outer structures. 
    Assuming galaxies at the same \minn{} have similar amount stars in the in-situ 
    component, it is of great interest to investigate the relation between their 
    environments and outer envelopes that are assembled at later time. 
    It is worth noting that, although a circular aperture is shown on 
    Fig.\ref{fig:m100_m10_color}, we always use elliptical apertures that follow the 
    average isophotal shape for photometry in this work.}
    And, within our choices of redshift and \mstar{} ranges, we can safely ignore 
    significant mass growth and structural evolution 
    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
    \citealt{Inagaki2015}; but also see \citealt{Bai2014}) 
    with our redshift and \mstar{} ranges.

@@

    Because of the caveats that apply to \texttt{hscPipe} measurements for bright 
    galaxies, we will use custom made software to measure the luminosity profiles of
    massive galaxies. 
    \update{
    As the first step, we select the initial sample of massive galaxies at $z < 0.5$
    from the HSC photometric catalog.}
    We will then use custom made software to re-measure luminosities for all galaxies 
    in this sample. 
    Based on Leauthaud\etal~(2016), most \logms{}$\geq 11.5$ galaxies should have 
    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag.
    So we first select all galaxies with $i_{\mathrm{HSC, cModel}} \leq 21.5$ 
    \footnote{We neglect the insignificant differences between the response curves of
    SDSS-$i$ and HSC-$i$ filters}
    in regions that have reached the required depth of \texttt{WIDE} survey in all 
    five bands. 
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects

@@

    Among the 116813 matched objects, 42696 are at $0.2 \leq z \leq 0.5$.
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    The majority of these redshifts come from either SDSS or BOSS data.  
    GAMA survey contributes another $\sim 14$\%. 
    For objects without external spec-$z$, we match them with the central galaxies 
    from \redm{} catalog using $2.0^{\arcsec}$ radius. 
    The matched objects with useful red-sequence photo-$z$ ($z_{\lambda}$) are also 
    included in the final sample of bright galaxies with reliable redshift between 
    $0.2 \leq z \leq 0.5$
    (will be referred as \texttt{hscZ}).
    As we will mention at the end of the paper, to ensure reasonable 
    \mstar{}-completeness at the high-\mstar{} end, and make sure the samples we 
    want to compare have well overlapped redshift distributions, we will focus on 
    the galaxies at $0.3 \leq z \leq 0.5$.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[bt!]
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_smf_new}
      \caption{\textbf{Left:} Difference between \mcmodel{} and \mtot{} for central
      	galaxies in halos smaller than $10^{14}$ M$_{\odot}$ (grey dots) and in
        halos larger than $10^{14}$ M$_{\odot}$ (red squares). 
        On average, \mcmodel{} underestimates the total stellar mass of massive 
        galaxies by 0.1 dex and the difference can exceed 0.2 dex. 
        Vertical histograms indicate the mass difference for galaxies with
        $11.6<$\logmtot{}$<11.9$. 
        \textbf{Right:}: Impact of using \mcmodel{} on the galaxy stellar mass
        function. 
        Dashed lines correspond to the SMF computed using \mcmodel{} as an estimate
        of the total luminosty whereas solid lines correspond to the SMF computed
        using the total luminosity from our 1-D profile modeling. 
        The impact on the SMF can exceed 0.2 dex for massive centrals living in
        halos larger than $10^{14}$ M$_{\odot}$ (red lines).}
      \label{fig:smf1}
  \end{figure*}

%           We compre the \mstar{} volume-density distributions of 
%      	  \rbcg{} (red) and \nbcg{} (black) galaxies using stellar mass based on 
%          \mcmodel{} (dash) and \mtot{} (solid) to highlight the increase of \mstar{}
%          due to different methods.  
%          Here we also show the volume-density distributions of the \texttt{S82-MGC} 
%          galaxies (green) to evaluate the \mstar{}-completeness. 
%          The vertical line highlight \logms{}$=11.6$ before correcting the \mstar{} using
%          total luminosity from 1-D profile.~~

@@

    Assuming that the \redm{} catalog correctly identifies all halos with 
    $M_{200m}\sim 1.0\times 10^{14} h^{-1} M_{\odot}$ in the current footprint,
    the unmatched massive galaxies from the above step should be dominated by central 
    galaxies of less massive halos and massive satellites galaxies.  
    \update{
    To select a purer sample of massive centrals in $M_{200m}<10^{14} h^{-1} M_{\odot}$
    halos, we identify and remove all galaxies within a cylinder region around the 
    the central galaxies in \redm{} catalog.
    We choose to use the $R_{200m}$ as the radius of the cylinder. 
    For each cluster, we convert the richness estimates into $M_{200m}$ using the 
    calibration in \citep{Simet2016}, then estimate the $R_{200m}$ using $M_{200m}$
    and the mass-concentration relation in \citep{Diemer2015}. 
    For the thickness of the cylinder, we use twice the uncertainty of the photometric 
    redshift error of each cluster.  
    At $0.3 < z < 0.5$, such uncertainty is between 0.015 to 0.025, which are more than 
    enough to exclude cluster member.}
    \song{The actual number waits to be updated}

    %\alexie{This is a rather strange procedure, I think we need to change it (referee and readers will complain!). What we really want to do is to remove any galaxies that have $r<R200$ in projection (from the galaxy with the highest value of Pcen) and remove galaxies within some deltaz of the cluster redshift. The cluster redshift is more well determined than the redshift estiamte of any cluster member. In short, what we are doing here is cutting out a cylindar arond the most likley BCG. The deltaz value can be motivated by the cluster redshift uncertainty from the redmapper papers. The only remaining question is then what radius to use around clusters. To get that number here is what we need to do. 1) Start with Eq 12 and Table 3 in Simet et al. For each cluster, assign a value of M200m (halo mass defined as 200 time background) to each cluster. 3) we then need to estimate the cluster radius R200m (or R200b, same thing). To do this, we need to use a mass-concentration relation. I'm pretty sure there is an easy command to do this in Python using the python package "colossus" by bendikt diemer. Download it and see if youc an get it to work. If it doens't look obvious after 30 min, I can do it on my end using my own code. But good for you to know how to do this. We can simply use the mass-concentration realtion from Benedikts work. 4) Now for every cluster you have R200m. And you define the low halo mass central sample as ones that are not within any cylindar around any cluster. Sorry, I know this might mean re-doing everything.....let's discuss by Skype if this is a major issue.}

@@

    \begin{itemize}
        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
            with $i_{\mathrm{cModel}} \leq 21.0$, good quality images and reliable 
            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
            data release. 
        \item \texttt{hscZ} sample: through matching the \texttt{hscPho} sample with 
            spectroscopic redshifts from surveys like SDSS/BOSS and GAMA, or accurate 
            red-sequence photometric redshift in the \redm{} catalog, we come up with 
            a large sample of bright galaxies with reliable redshift information. 
        \item \rbcg{} sample: we select a sample of 375 galaxies at $0.2 \leq z \leq 0.5$
            that are identified as central galaxies in $\lambda > 30$ \redm{} clusters. 
            The most reliable ones ($P_{\mathrm{Cen}} >0.7$) among 
            them will represent the central galaxies in very massive halos
            (\logmh{}$\geq 14.0$). 
        \item \nbcg{} sample: after excluding all the galaxies that are close to any 
            \redm{} clusters in both radial and redshift directions from the 
            \texttt{hscZ} sample, we have 29973 bright galaxies at $0.2 \leq z \leq 0.5$.
            With the help of \mstar{} estimates via SED fitting (see Section 
            \ref{ssec:isedfit}), we consider the massive ones among them as the 
            candidates of central galaxies in halos with \logmh{}$<14.0$.  
        \item To compare the \rbcg{} and \nbcg{} samples carefully, we will focus on 
            the redshift range at $0.3 \leq z \leq 0.5$ where their redshift 
            distributions greatly overlap and both samples have acceptable
            \mstar-completeness (see Section \ref{ssec:s82}).  
            \update{Although we use the $\lambda > 30$ sample for structural comparison, 
            in the Appendix.\ref{app:robust}, we show that the results will not change 
            if we include central galaxies of $20 < \lambda \leq 30$ clusters in the 
            \rbcg{} sample.}
    \end{itemize}

@@

    Finally, we run \texttt{Ellipse} on the background-corrected image following similar 
    strategy of \citep{Li2012}.
    In short, we start with free centroid and shape of each isophote, then gradually 
    constrain their behaviors, and eventually extract 1-D surface brightness profile 
    along the major axis using isophotes with fixed centroid and shape.
    The 4th Fourier modes are included to fit the isophote better. 
    In this way, we can extract the radial changes of the centroid, ellipticity, 
    position angle, and average isophotal distortions (more ``disky'' or ``boxy'', 
    e.g.\ \citealt{Kormendy2009}) along with the surface brightness profile.  
    Fig.\ref{fig:ellipse} shows an example of the 1-D surface brightness and 
    ellipticity profile for a massive galaxy at $z\sim0.2$ along with its masked 
    image and a subset of isophotes.  
    Appendix.\ref{app:A} includes more details about the \texttt{Ellipse} procedure.

@@

    We construct five band SED using the forced-photometry \cmodel{} magnitude corrected 
    for the Galactic extinction. 
    As for the photometric error, the current \cmodel{} photometry underestimates 
    the flux errors of bright galaxies as it only includes statistical error, not the 
    systematic uncertainties in the model-fitting process.  
    From tests of synthetic objects, we find that the average accuracy of \cmodel{} 
    photometry for bright galaxy is roughtly at 1\% level. 
    Therefore, we supply \texttt{iSEDFit} with simplified flux errors assuming $S/N = 100$ 
    for $riz$ bands, and $S/N = 80$ for $gY$ bands (on average, images in $gY$ bands are 
    shallower in depth and/or have higher background noise).  
    The typical uncertainty of \logms{} for both samples is around 0.08-0.10 dex at the 
    high-\mstar{} end. 
    Please see Appendix.\ref{app:B} for more detailed discussions of the SED fitting
    results.  
    %In Fig.~3, we show an example of SED fitting result. 
    %\song{Not sure if we need to show one example, but put one here for now.}

@@

@@

    Using the best-fit stellar mass from \texttt{iSEDFit} (referred as \mcmodel{}), 
    we estimate the average \m2l{} in $i$-band, then use that \m2l{} to convert the 
    1-D luminosity density profiles into stellar mass density profiles; and 
    also convert the luminosity within 10 and 100 kpc apertures into 
    corresponding stellar mass estimates (referred as \minn{} and \mtot{}). 
    From now, we use \mtot{} as the new proxy of ``total'' stellar mass of these 
    galaxies.  
    And we also derive the $k$-corrected luminosity and colors from the results.
    In Appendix.\ref{app:B}, we also show the outputs like the average stellar age, 
    metallicity, and internal dust extinction all behave reasonably for both 
    samples, but will not use them for further scientific analysis.

@@

    And, we should mention that our approach is in principle very similar to the 
    one adopted by the GAMA survey (\citealt{Taylor2011}), where they start with 
    \mstar{} estimated using average \m2l{} from SED fitting results of
    PSF-matched aperture photometry, and later correct it with better estimate 
    of total luminosity.  
    However, the GAMA survey relied on multi-band single-\ser model fitting on 
    the SDSS images to get total luminosity (\citealt{Kelvin2012}). 
    It is therefore interesting to compare the \mstar{} (\mgama{} v.s. \mtot{})
    estimates for galaxies in common, given the differences in data and method. 
    Please see the Appendix.\ref{app:C} for more details. 
    In short, we notice systematic differences between the two \mstar{} estimates, 
    and it is likely that the GAMA models miss fluxes in the stellar halo that 
    is beyond the depth of SDSS image.

    \update{In Appendix.\ref{app:basic}, we summarize the basic statistics of 
    the \rbcg{} and \nbcg{} samples.  In general:}
